Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2020-08-25 Scripts/Initial_Analysis.Rmd
reversed scale of Fig 3

# Paths <- paste(my_path("R",extra_path = "Emergence_2005"),Taxon_List_emer,"_emergence.txt",sep="")

@@

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid= eez_id ,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  filter(metric != "n_taxa")

@@

ggplot(subset(eez_d_hist, tresh == "Tresh_one")) +
  geom_density(
    aes(
      x = value,
      fill = tresh
    ),
    bins = 10,
    alpha = 0.8
  ) +
  facet_wrap(~metric,
             scales = "free") +
  scale_fill_viridis(discrete = T) +
  my_ggtheme_p() +
  ggsave("./Figures/hist_mean.png",
         width = 6,
         height = 6,
         units = "in"
  )

@@

grey_eez <- World_eez_sf %>% 
  filter(!eezid %in% eez_d_hist$eezid)

@@

  tresh_list <- c("Tresh_one","Tresh_two")
  name_save <- paste("./Figures/emer_map_par_",tresh_list[i],".png",sep = "")

  World_map_nemer <- World_map_nemer %>% 
    filter(
      tresh ==  tresh_list[i], 
      variable == "value"
    )

  map <- World_eez_sf %>% 
    left_join(eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = value
      ),
      color =  "white",
      size = 0.1
    ) +
    geom_sf(data = World_map_nemer,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    annotate("text", 
             x =(c(-85.5,-30,25,81,136)+5),
             y = -93.5,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis(
      limits = c(2000,2100),
      breaks = seq(2000,2100,25)
    ) +
    my_ggtheme_m() +
    ggsave(name_save,
           width = 12,
           height = 10,
           units = "in"
    )

>>>>

Paths <- paste(my_path("R",extra_path = "Emergence_2005"),Taxon_List_emer,"_emergence.txt",sep="")

@@

# Per EEZs
Eez_d_hist <- Eme_Res %>% 
  group_by(eezid= eez_id ,sau_fishing_entity,tresh) %>% 
  # summarise(n_tax = length(unique(taxon_key))) %>% 
  summarise(
    mean_yr = mean(emerging_yr,na.rm=T),
    sd_yr = sd(emerging_yr,na.rm=T),
    n_taxa = length(unique(taxon_key))
    ) %>% 
  gather("metric","value",mean_yr:n_taxa) %>% 
  filter(metric != "n_taxa") %>% 
  mutate(
    reverse = abs(value-2100)  + 2000
  )

@@

ggplot(subset(Eez_d_hist, tresh == "Tresh_one")) +
  geom_density(
    aes(
      x = value,
      fill = tresh
    ),
    bins = 10,
    alpha = 0.8
  ) +
  facet_wrap(~metric,
             scales = "free") +
  scale_fill_viridis(discrete = T) +
  my_ggtheme_p() +
  ggsave("./Figures/hist_mean.png",
         width = 6,
         height = 6,
         units = "in"
  )

@@

grey_eez <- World_eez_sf %>% 
  filter(!eezid %in% Eez_d_hist$eezid)

@@

  tresh_list <- c("Tresh_one","Tresh_two")
  name_save <- paste("./Figures/emer_map_rev_",tresh_list[i],".png",sep = "")

  World_map_part <- World_map_nemer %>% 
    filter(
      tresh ==  tresh_list[i], 
      variable == "value"
    )

  map <- World_eez_sf %>% 
    left_join(Eez_d_hist,
              by = "eezid") %>% 
    filter(tresh == tresh_list[i],
           metric == "mean_yr") %>% 
    ggplot() +
    geom_sf(
      aes(
        fill = reverse
      ),
      color =  "white",
      size = 0.1
    ) +
    # Inlcude the participation of species
    geom_sf(data = World_map_part,
            aes(fill = participation+2000),
            color =  "white",
            size = 0.1
            ) +
    # grey maps
    geom_sf(data = grey_land, aes(),fill = "grey50", color =  "white",size = 0.1) +
    geom_sf(data = grey_eez, aes(),fill = "grey50", color =  "white",size = 0.1) +
    annotate("text", 
             x =(c(-85.5,-30,25,81,136)+5),
             y = -93.5,
             # x =(c(-8500000,-3000000,2500000,7500000,12800000)),
             # y = -9050000,
             label = c(0,25,50,75,100), 
             color="black", 
             size=3, 
             angle=0, 
             # fontface="bold",
             hjust=0) +
    scale_fill_viridis(
      limits = c(2000,2100),
      breaks = seq(2000,2100,25),
      labels = seq(2100,2000,-25),
      direction = -1
    ) +
    my_ggtheme_m() +
    ggsave(name_save,
           width = 12,
           height = 10,
           units = "in"
    )
